Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-10 prop_letter.tex
prop_letter.tex \section{Born} Updating...

\begin{thm}\label{thm:QRVPM2QIVPM-3}In a Hilbert space of dimension~$d\le3$,
if $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ subject to the
following constraints:\begin{subequations}\label{eq:iota-constraints}
\begin{eqnarray}
 &  & \iota(0)=\imposs\,,\\
 &  & \iota(1)=\necess\,,\\
 &  & \iota\left(1-x\right)=\necess-\iota\left(x\right)\,,
\end{eqnarray}
\end{subequations}and satisfying for any numbers~$x_{0}$ and $x_{1}\in\left[0,1\right]$,
$x_{0}+x_{1}\in\left[0,1\right]$ implies
\begin{equation}
\iota\left(x_{0}+x_{1}\right)\subseteq\iota\left(x_{0}\right)+\iota\left(x_{1}\right)\,.\label{eq:iota-add}
\end{equation}
Then, $\iota\circ\mu:\events\rightarrow\mathscr{I}$ is always a QIVPM
for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.\end{thm}

@@

\begin{thm}The following two statements are equivalent:
\begin{enumerate}
\item \label{enu:iota-subject-to}The function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
subject to Eqs.~(\ref{eq:iota-constraints}) and satisfying for any
three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
$x_{0}+x_{1}+x_{2}\in\left[0,1\right]$ implies
\begin{equation}
\begin{aligned} & \iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\\
\subseteq{} & \iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.
\end{aligned}
\label{eq:iota-Inclusion}
\end{equation}
\item \label{enu:iota-mu-QIVPM}The composited function~$\iota\circ\mu:\events\rightarrow\mathscr{I}$
is always a QIVPM for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
on any Hilbert space~$\Hilb$.
\end{enumerate}
\end{thm}

@@

Since $\iota_{1}\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$ is not
a QIVPM, we know $\iota_{1}$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}).
In order to find a function~$\iota$ satisfying Eq.~(\ref{eq:iota-Inclusion}),
we decompose it into two functions: its left-end and right-end~$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
They both map from a unit interval to another unit interval. Eq.~(\ref{eq:iota-Inclusion})
then implies that $\iotal$ is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$,
and $\iotar$ is Wright-concave, i.e., $\iotar\left(x_{0}+x_{1}+x_{2}\right)+\iotar\left(x_{2}\right)\le\iotar\left(x_{0}+x_{2}\right)+\iotar\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992,Brzdek_2014}.
It is well-known that a Wright-convex function is midpoint-convex
or Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992},
i.e., we have
\begin{equation}
\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\,.
\end{equation}
Furthermore, a midpoint-convex function is either continuous on $\left(0,1\right)$
or Lebesgue non-measurable~\citep{Blumberg_1919,Sierpinski1920,RobertsVarberg1973}.
When $\iotal$ is Lebesgue non-measurable,

When $\iotal$ is continuous, the range of $\iota$ either is $\left\{ \necess,\imposs,\unknown\right\} $
or contains uncountably many intervals.

>>>>

\begin{thm}\label{thm:QRVPM2QIVPM-3}In a Hilbert space of dimension~$d\le3$,
if $\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is subject to the
following constraints:\begin{subequations}\label{eq:iota-constraints}
\begin{eqnarray}
 &  & \iota(0)=\imposs\,,\\
 &  & \iota(1)=\necess\,,\\
 &  & \iota\left(1-x\right)=\necess-\iota\left(x\right)\,,
\end{eqnarray}
\end{subequations}and satisfies that for any numbers~$x_{0}$ and
$x_{1}\in\left[0,1\right]$, $x_{0}+x_{1}\in\left[0,1\right]$ implies
\begin{equation}
\iota\left(x_{0}+x_{1}\right)\subseteq\iota\left(x_{0}\right)+\iota\left(x_{1}\right)\,.\label{eq:iota-add}
\end{equation}
Then, $\iota\circ\mu:\events\rightarrow\mathscr{I}$ is always a QIVPM
for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.\end{thm}

@@

\begin{thm}\label{thm:iota-statements}The following two statements
are equivalent:
\begin{enumerate}
\item \label{enu:iota-subject-to}The function~$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is subject to Eqs.~(\ref{eq:iota-constraints}) and satisfies that
for any three numbers~$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
$x_{0}+x_{1}+x_{2}\in\left[0,1\right]$ implies
\begin{equation}
\begin{aligned} & \iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\\
\subseteq{} & \iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)\,.
\end{aligned}
\label{eq:iota-Inclusion}
\end{equation}
\item \label{enu:iota-mu-QIVPM}The composited function~$\iota\circ\mu:\events\rightarrow\mathscr{I}$
is always a QIVPM for any quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$
on any Hilbert space~$\Hilb$.
\end{enumerate}
\end{thm}

@@

Since $\iota_{1}\circ\mu_{\rho_{1}}^{\mathrm{\mathrm{B}}}$ is not
a QIVPM, we know $\iota_{1}$ doesn't satisfy Eq.~(\ref{eq:iota-Inclusion}).
In order to find a function~$\iota$ satisfying Eq.~(\ref{eq:iota-Inclusion}),
we decompose it into two functions: its left-end and right-end~$\left[\iotal\left(x\right),\iotar\left(x\right)\right]=\iota\left(x\right)$.
By Eq.~(\ref{eq:iota-Inclusion}), the left-end~$\iotal:\left[0,1\right]\rightarrow\left[0,1\right]$
is Wright-convex, i.e., $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$,
and the right-end~$\iotar:\left[0,1\right]\rightarrow\left[0,1\right]$
is Wright-concave, i.e., $\iotar\left(x_{0}+x_{1}+x_{2}\right)+\iotar\left(x_{2}\right)\le\iotar\left(x_{0}+x_{2}\right)+\iotar\left(x_{1}+x_{2}\right)$~\citep{Wright1954,RobertsVarberg1973,PecaricTong1992,Brzdek_2014}.
It is well-known that a Wright-convex function is midpoint-convex
or Jensen-convex~\citep{Klee_1956,Kenyon_1956,RobertsVarberg1973,PecaricTong1992},
i.e., we have
\begin{equation}
\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\,.
\end{equation}
Together with the fact that $\iotal$ maps to a bounded interval~$\left[0,1\right]$,
$\iotal$ must be continuous on the unit open interval~$\left(0,1\right)$~\citep{Jensen_1906,RobertsVarberg1973}
which implies the number of intervals that $\iota$ maps to must be
uncountable.

\begin{thm}If $\iota$ satisfies the Statements in Thm.~\ref{thm:iota-statements},
then the range of $\iota$ either is $\left\{ \necess,\imposs,\unknown\right\} $
or contains uncountably many intervals.\end{thm}
